Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-03-12 manuscript/supplementaryRW.Rmd
remove figure mort7_10_iqrOver.png

@@

@@

## Recruitment species composition

```{r recrStand7, echo=FALSE, fig.cap="Mean Shannon index per site for the recruitment  and at the stand level both for observed and simulated values. NOTE: The recruitment treshold recruitment for treshold 7 cm in the empirical data has several sites with no recruitment or no data and the Shannon index for those sites is NA", out.width='100%'}
knitr::include_graphics(here::here("figures", "recruitmentAdultRichness7.png"))
```

```{r recrStand10, echo=FALSE, fig.cap="Mean Shannon index per site for the recruitment  and at the stand level both for observed and simulated values. NOTE: The recruitment treshold recruitment for treshold 10 cm in the empirical data has several sites with no recruitment or no data and the Shannon index for those sites is NA", out.width='100%'}
knitr::include_graphics(here::here("figures", "recruitmentAdultRichness10.png"))
```

@@

## Mortality

```{r mortality12 , echo=FALSE, fig.cap="Interquartile range of the ratio between 7 and 10cm recruitment and the overestimation proportion (sim-obs/obs) for the mean recruitment trees per model across sites and samples", out.width='70%'}
knitr::include_graphics(here::here("figures", "mort7_10_iqrOver.png"))
```

tabletrends <- readr::read_csv(here::here("figures", "mort7_10_trends.csv"))
kable(tabletrends,  format = "markdown", caption = "Models trends in mortality between and 10cm.")
```

>>>>

```{r recrStand7, echo=FALSE, fig.cap="Mean Shannon index per site at recruitment and at the stand level both for observed and simulated values for the diameter threshold of 7cm", out.width='100%'}
knitr::include_graphics(here::here("figures", "recruitmentAdultRichness7.png"))
```

```{r recrStand10, echo=FALSE, fig.cap="Mean Shannon index per site at recruitment and at the stand level both for observed and simulated values for the diameter threshold of 10cm", out.width='100%'}
knitr::include_graphics(here::here("figures", "recruitmentAdultRichness10.png"))
```

### Mortality

tabletrends <- readr::read_csv(here::here("figures", "mort7_10_trends.csv"))
kable(tabletrends,  format = "markdown", caption = "Models trends in mortality between 7 and 10cm, and the ingrowth at 7cm, based in the mean oer site .")
```

\newpage

@@

\newpage

@@

@@
